Behavior-Driven Development in Haskell

### 2012-10-20 paper.tex
Emphasis first use of BDD

In this section we show how to do BDD in Haskell, how to reuse pieces
of specification, and how to use Doctest and Hspec in combination with
Cabal's test feature.

>>>>

In this section we show how to do \emph{behavior-drive development
(BDD)} in Haskell, how to reuse pieces
of specification, and how to use Doctest and Hspec in combination with
Cabal's test feature.
